Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-29 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:29	19:21:57	(Sat29.Aug)

A much less complex alternative to MVDR is the low complexity adaptive (LCA) beamformer. It iterates through a set of $P$ windows and selects the window $p$ that best fulfills the minimum variance criteron:
%
\begin{align}
\underset{p}{\argmin}\, E\{|z[n]|^2\} = \underset{p}{\argmin}\, E\big\{|\w_{p}\H\x[n]|^2\big\}\nn
\qquad\text{subject to}\qquad \w\H\a_\phi = 1.\label{eq_lca_definition}
\end{align}\label{lca_criterion}
%
Note how closely LCA is related to the MVDR definition in \eq{eq_mvdr_definition}. The optimization criterion and constraint is the same, but LCA has a finite and discrete solutionspace for the weights. As will be demonstrated in section \ref{lca_window_function}, this can be done because a robustified MVDR implementation seems to be constrained to window functions similar to the conventional ones.

>>>>

A much less complex alternative to MVDR is the low complexity adaptive (LCA) beamformer. It iterates through a set of $P$ windows and selects the window $p$ that best fulfills the minimum variance criteron:
%
\begin{align}
\underset{p}{\argmin}\, E\{|z[n]|^2\} = \underset{p}{\argmin}\, E\big\{|\w_{p}\H\x[n]|^2\big\}\nn
\qquad\text{subject to}\qquad \w\H\a_\phi = 1.\label{eq_lca_definition}
\end{align}\label{lca_criterion}
%
Note how closely LCA is related to the MVDR definition in \eq{eq_mvdr_definition}. The optimization criterion and constraint is the same, but LCA has a finite and discrete solutionspace for the weights. As will be demonstrated in section \ref{lca_window_function}, LCA will perform similarly because a robustified MVDR implementation seems to be constrained to window functions similar to the ones we let LCA choose from.
